Practical Optional Types for Clojure

### 2015-02-24 formal-model.tex
todo
clojure reference
model

@@

The propositions inform conditionals on what they can assume down the then and else
branches if the expression is used as a test.
The object is a possibly-empty symbolic representation of the expression.

Syntax is given in figure~\ref{main:figure:termsyntax}. Expressions include variables, values,
application, abstractions, conditionals, do (sequencing) expressions and let expressions.
All binding forms introduce fresh variables.

Values include booleans, \nil{}, class literals, keywords (written with a : prefix like \clj{:a}), 
constants and closures.  \false{} and \nil{} are logically false; all other values are logically true.

@@

Propositions are identical to~\cite{TF10}; positive and negative type propositions, implications,
conjunctions, disjuctions, trivial and impossible propositions.
Type propositions contain a non-empty object which it claims type information about.

@@

>>>>

\label{sec:formal}

@@

The propositions capture what can be assumed if an expression tests as logically true or false
respectively. The object is a possibly-empty symbolic representation of the expression.

Syntax is given in figure~\ref{main:figure:termsyntax}. Expressions include variables, values,
application, abstractions, conditionals and let expressions.
All binding forms introduce fresh variables.

Values include booleans, \nil{}, class literals, keywords (written with a : prefix like \makekw{a}), 
constants and closures.  \false{} and \nil{} are logically false; all other values are logically true.

@@

Propositions are identical to~\cite{TF10}---positive and negative type propositions, implications,
conjunctions, disjuctions, trivial and impossible propositions.
Type propositions contain a non-empty object which it claims type information about.

@@

% TODO semantics
